List of publications

### 2025-03-13 report/index.qmd
index

---
title: "Liste des enquêtes"
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    number-depth: 2
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
date: today
date-format: long
params:
  file: "../data/IPI.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---

>>>>

---
title: "List of publications"
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    number-depth: 2
    code-links:
      - text: AQLT/publishTC.wp
        icon: github
        href: https://github.com/AQLT/publishTC.wp
date: today
date-format: long
params:
  file: "../data/IPI.yml"
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
---
